FraCaS: Temporal Analysis

### 2020-06-09 paper2020/paper.tex
intro

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the
years~\citep{dowty:2012,prior:2003,steedman:2000,higginbotham:2009,fernando:2015}. The
semantics of tense and aspect has been also central in the study of
Natural Language Inference (NLI)\todo{citation?}. The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7). This part
of the FraCaS test suite has been notoriously difficult to tackle. In
fact, all the computational systems ran on the FraCaS test suite so
far skip this section. Additionally, they also skip the anaphora
and ellipsis sections, with the exception of the system presented by
\citet{bernardy_type_2017,bernardy_wide_2019}, which offers a complete whole run of the
FraCaS test suite, excluding the temporal section. In this
paper, we take up the challenge of providing a computationally viable
account of tense and aspect to deal with the notorious section 8\todo{or 7? 8 was not discussed previously} of
the FraCaS test suite. Our account is not meant to be a theoretically
full account of tense and aspect, but rather an account that is driven by the
need to cover the test suite in a way that is general enough to
capture the test suite examples. The account is evaluated on the
entailment properties of various temporal and aspectual examples, as
given by the test suite. As such, we are not getting into the
discussion of how tense and aspect might affect grammaticality or
infelicitousness of various sentences. We take the sentences of the
FraCaS suite to be syntactically correct and the entailment patterns they
are annotated with valid.

>>>>

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the
years~\citep{dowty:2012,prior:2003,steedman:2000,higginbotham:2009,fernando:2015}. The
semantics of tense and aspect has been also considered in the study of
Natural Language Inference (NLI)\todo{citation?}. The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7). This part
of the FraCaS test suite has been notoriously difficult to tackle. In
fact, all the computational systems ran on the FraCaS test suite so
far skip this section. Additionally, they also skip the anaphora
and ellipsis sections, with the exception of the system presented by
\citet{bernardy_type_2017,bernardy_wide_2019}, which offers a complete whole run of the
FraCaS test suite, excluding the temporal section. In this
paper, we take up the challenge of providing a computationally viable
account of tense and aspect to deal with the notorious section 7\todo{or 7? 8 was not discussed previously} of
the FraCaS test suite. Our account is not meant to be a theoretically
full account of tense and aspect, but rather an account that is driven by the
need to cover the test suite in a way that is general enough to
capture the test suite examples. The account is evaluated on the
entailment properties of various temporal and aspectual examples, as
given by the test suite. As such, we are not getting into the
discussion of how tense and aspect might affect grammaticality or
infelicitousness of various sentences. We take the sentences of the
FraCaS suite to be syntactically correct and the entailment patterns they
are annotated with valid.
